ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-19 paper/body.tex
s

Our default choice for the $\text{dist}(\cdot)$ in both cases is the L1 Norm.

>>>>

Our default choice for the $\text{dist}(\cdot)$ in both cases is the L1 Norm, which is consistent with the common choice for evaluating counterfactuals with respect to the closeness desideratum~\citep{pawelczyk2021carla,pawelczyk2022probabilistically}.
